---
title: "Exploration: Data Analysis"
author: "Gary Nguyen"
date: "2021-05-29"
---

```{r library}
library(tidyverse)
library(glue)
library(here)
library(ggplot2)
library(ggthemes)
```

```{r load_train_test}
raw_train <- readr::read_csv(
  file.path(data_dir, 'train_v2.csv'), col_types = col_types
  )
raw_test <- read_csv(
  file.path(data_dir, 'test_v2.csv'), col_types = col_types
  )

train <- prc_ggl_data(raw_train, select_cols = FALSE)
test <- prc_ggl_data(raw_test, select_cols = FALSE)
```

```{r processed_train}
# Training Set:
train <- train %>% 
  mutate(totalTransactionRevenue = ifelse(is.na(totalTransactionRevenue), 0, totalTransactionRevenue)) %>% 
  mutate(purchased = ifelse(totalTransactionRevenue > 0, 1, 0))

test <- test %>% 
  mutate(totalTransactionRevenue = ifelse(is.na(totalTransactionRevenue), 0, totalTransactionRevenue)) %>% 
  mutate(purchased = ifelse(totalTransactionRevenue > 0, 1, 0))
```

```{r save_data_with_purchase}
saveRDS(train, file.path(data_dir, 'main_train.rds'))
saveRDS(test, file.path(data_dir, 'main_test.rds'))
```

#### 1. Check if there is any columns with only one value

In the training and test set, 18 features only have 1 values. For the modelling purpose, I removed these features.

```{r check_unique_val_train}
columns_val_num <- apply(train, 2, function(x) length(unique(x)))
column_names <- names(columns_val_num)

values_train <- tibble(
  'columns' = column_names,
  'num_unique_values' = columns_val_num
) %>% arrange(num_unique_values)

values_train
```

```{r check_unique_val_test}
columns_val_num <- apply(test, 2, function(x) length(unique(x)))
column_names <- names(columns_val_num)

values_test <- tibble(
  'columns' = column_names,
  'num_unique_values' = columns_val_num
) %>% arrange(num_unique_values)

values_test
```

#### 2. Check if there is any columns with NA values

In the training set, there are 18 columns with NA values, and specifically, `totalTransactionRevenue` has most NA values.
In the test set, there are 14 columns with NA values.

```{r col_na_train}
num_na <- colSums(is.na(train))
column_names <- names(num_na)

col_na_train <- tibble(
  'columns' = column_names,
  'num_na' = num_na
) %>% arrange(desc(num_na))

col_na_train
```

```{r col_na_test}
num_na <- colSums(is.na(test))
column_names <- names(num_na)

col_na_test <- tibble(
  'columns' = column_names,
  'num_na' = num_na
) %>% arrange(desc(num_na))

col_na_test
```

### 3. Referral has a higher chance of paying

```{r purchased_by_channels}
p <- train %>% 
  select(fullVisitorId, channelGrouping, purchased) %>% 
  group_by(channelGrouping, purchased) %>% 
  tally() %>% 
  ungroup() %>%
  mutate(purchased = as.character(purchased)) %>% 
  ggplot(aes(x = channelGrouping, y = n, fill = purchased)) +
  geom_bar(position = position_dodge2(width = 0.9, preserve = 'single'), stat = 'identity') +
  coord_flip() +
  theme_hc() +
  xlab('Visits') +
  ylab('Channel') +
  ggtitle('Visit Types by Channels')

print(p)

ggsave(file.path(here::here(), 'figures/purchased_by_channels.png'), p)
```

### 4. High fullVisitorId has more purchased?

Question: Do high `fullVisitorId` make you act differently?

```{r fullVisitorId_density_no_transform}
p <- train %>% 
  mutate(fullVisitorId = as.numeric(fullVisitorId)) %>% 
  ggplot(aes(x = fullVisitorId, fill = purchased)) +
  geom_density(alpha = 0.5, aes(fill = factor(purchased))) + 
  labs(title = 'Density of purchased, given fullVisitorId (No Transform)') +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) + 
  theme_grey() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  xlab('fullVisitorId') +
  ylab('Density') +
  theme_hc()

print(p)
ggsave(file.path(here::here(), 'figures/fullVisitorId_density_no_transform.png'), p)
```

Probably not, because a transformation of `^(1/3)` makes them act the same.

```{r fullVisitorId_density}
p <- train %>% 
  mutate(fullVisitorId = as.numeric(fullVisitorId)) %>% 
  ggplot(aes(x = fullVisitorId^(1/3), fill = purchased)) +
  geom_density(alpha = 0.5, aes(fill = factor(purchased))) + 
  labs(title = 'Density of purchased, given fullVisitorId (Transformed)') +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) + 
  theme_grey() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  xlab('fullVisitorId') +
  ylab('Density') +
  theme_hc()

print(p)
ggsave(file.path(here::here(), 'figures/fullVisitorId_density.png'), p)
```

### 5. Does higher visitNumber mean higher likelihood of purchase?

It seems like higher number of visits does mean higher likelihood of transaction.

```{r purchased_num_visits}
p <- train %>% 
  ggplot(aes(x = log(visitNumber), fill = purchased)) +
  geom_density(alpha = 0.5, aes(fill = factor(purchased))) + 
  labs(title = 'Density of purchased, given visitNumber') +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) + 
  theme_hc() +
  xlab('Log of Number of Visits') +
  ylab('Density')

print(p)
ggsave(file.path(here::here(), 'figures/purchased_num_visits.png'), p)
```

### 6. Does Visit Start Time influence purchase?

It seems like more recent visits mean fewer purchases.

```{r purchased_start_time}
p <- train %>% 
  ggplot(aes(x = visitStartTime, fill = purchased)) +
  geom_density(alpha = 0.5, aes(fill = factor(purchased))) + 
  labs(title = 'Density of purchased, given visitStartTime') +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  theme_hc() +
  xlab('Visit Start Time') +
  ylab('Density')

print(p)
ggsave(file.path(here::here(), 'figures/purchased_start_time.png'), p)
```

### 7. Does the Type of device matter?

Desktops have a higher likelihood to make a purchase.

```{r purchased_by_device_cat}
p <- train %>% 
  group_by(deviceCategory, purchased) %>% 
  tally() %>% 
  ungroup() %>% 
  mutate(purchased = as.character(purchased)) %>% 
  ggplot(aes(x = deviceCategory, y = n, fill = purchased, label = n)) +
  geom_bar(stat = 'identity') +
  geom_text(vjust = -0.5, size = 3) +
  theme_hc() +
  xlab('Device Category') +
  ylab('Count') +
  ggtitle('Purchase by Device Category')

print(p)
ggsave(file.path(here::here(), 'figures/purchased_by_device_cat.png'), p)
```

### 8. Geographic Analysis: Continent

The Americas (naturally) has the highest number of purchase-related visits.

```{r purchased_by_continent}
p <- train %>% 
  group_by(purchased, continent) %>% 
  tally() %>% 
  ungroup() %>% 
  mutate(purchased = as.character(purchased)) %>% 
  ggplot(aes(x = continent, y = n, fill = purchased, label = n)) +
  geom_bar(stat = 'identity', position = position_dodge2(width = 0.9, preserve = 'single')) +
  theme_hc() +
  xlab('Continent') +
  ylab('Count') +
  ggtitle('Purchase by Continent')

print(p)
ggsave(file.path(here::here(), 'figures/purchased_by_continent.png'), p)
```

### 9. Look at Total Hits

High number of hits signals likelihood to make a purchase.

```{r purchased_by_hits}
p <- train %>% 
  mutate(hits = as.numeric(hits)) %>% 
  ggplot(aes(x = log(hits), fill = purchased)) +
  geom_density(alpha = 0.5, aes(fill = factor(purchased))) + 
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) + 
  theme_hc() +
  ggtitle('Density of Purchased, Given log(hits)') +
  xlab('log(hits)') +
  ylab('Density')

print(p)
ggsave(file.path(here::here(), 'figures/purchased_by_hits.png'), p)
```

### 10. Look at Total Hits

```{r purchased_by_pageviews}
p <- train %>% 
  mutate(pageviews = as.numeric(pageviews)) %>% 
  ggplot(aes(x = log(pageviews), fill = purchased)) +
  geom_density(alpha = 0.5, aes(fill = factor(purchased))) + 
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) + 
  theme_hc() +
  ggtitle('Density of Purchased, Given log(pageviews)') +
  xlab('log(pageviews)') +
  ylab('Density')

print(p)
ggsave(file.path(here::here(), 'figures/purchased_by_pageviews.png'), p)
```








